\plaintitle

### 2017-04-27 statistical-quorum.tex
fixed math typo

For our purposes, we make a natural choice,
\begin{align}\label{eq6}
\lambda (t) = \lambda_0 {(\gamma)}^{-\frac{t}{K_i/N_i}},
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\lambda_0 =$] a time-averaged rate of vote arrivals (preferably over a unit of time that sufficiently smooths the historical rate),
\item[$\gamma =$] a decay factor ($0 < \gamma < 1$) ideally tuned to fit real historical data for the community via a regression analysis.
\end{itemize}
\end{description}
Now, for example, to upper bound with $95\%$ probability the remaining number of votes still pending, we solve for $\hat{K_i}$ to satisfy the following inequality:
\begin{align}\label{eq7}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{\gamma}}}\\
& \geq 95\% \nonumber
\end{align}
Upon solving for $\hat{K_i}$, we set $N_i = \alpha_i + \beta_i + \hat{K_i}$, and can proceed to check for a statistical quorum.

@@

\subsection{Derivation of Eq. \eqref{eq6}}
The properties we desire for $\lambda(t)$ are:
\begin{description}
\begin{itemize}
\item[$(1)$] as $K_i \rightarrow 0$, the rate of incoming votes should drop exponentially and should be independent of $N_i$,
\item[$(2)$] as $t \rightarrow \infty$, the rate of incoming votes should drop exponentially.
\end{itemize} 
\end{description}
Setting $\lambda (t) = \lambda_0 {(\gamma)}^{-\frac{t}{K_i/N_i}}$ satisfies these constraints while still allowing for the exact rate to be tunable.

\subsection{Derivation of Eq. \eqref{eq7}}
Using $\lambda (t) = \lambda_0 {(\gamma)}^{-\frac{t}{K_i/N_i}}$, we have
\begin{align*}
\lim_{t \rightarrow \infty} \Lambda (t) &=\int _{0}^{\infty}\lambda (t)\mathrm{d}t\\
&= \int _{0}^{\infty} \lambda_0 {(\gamma)}^{-\frac{t}{K_i/N_i}} \mathrm{d}t\\
&= \lambda_0 \frac{K_i/N_i}{\ln{\gamma}}.
\end{align*}
Thus, 
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t) = n\right) = \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{\gamma}}},
\end{align*}
and
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{\gamma}}}.
\end{align*}
\end{document}

>>>>

For our purposes, we make a natural choice,
\begin{align}\label{eq6}
\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}},
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\lambda_0 =$] a time-averaged rate of vote arrivals (preferably over a unit of time that sufficiently smooths the historical rate),
\item[$\gamma =$] a decay factor ($0 < \gamma < 1$) ideally tuned to fit real historical data for the community via a regression analysis.
\end{itemize}
\end{description}
Now, for example, to upper bound with $95\%$ probability the remaining number of votes still pending, we solve for $\hat{K_i}$ to satisfy the following inequality:
\begin{align}\label{eq7}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}}\\
& \geq 95\% \nonumber
\end{align}
Upon solving for $\hat{K_i}$, we set $N_i = \alpha_i + \beta_i + \hat{K_i}$, and can proceed to check for a statistical quorum.

@@

\subsection{Derivation of Eq. \eqref{eq6}}
The properties we desire for $\lambda(t)$ are:
\begin{description}
\begin{itemize}
\item[$(1)$] as $K_i \rightarrow 0$, the rate of incoming votes should drop exponentially and should be independent of $N_i$,
\item[$(2)$] as $t \rightarrow \infty$, the rate of incoming votes should drop exponentially.
\end{itemize} 
\end{description}
Setting $\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}}$ for $0 < \gamma < 1$ satisfies these constraints while still allowing for the exact rate to be tunable.

\subsection{Derivation of Eq. \eqref{eq7}}
Using $\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}}$, we have
\begin{align*}
\lim_{t \rightarrow \infty} \Lambda (t) &=\int _{0}^{\infty}\lambda (t)\mathrm{d}t\\
&= \int _{0}^{\infty} \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}} \mathrm{d}t\\
&= \lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}.
\end{align*}
Thus, 
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t) = n\right) = \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}},
\end{align*}
and
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}}.
\end{align*}
\end{document}
